---
title: "Iteration and list columns"
output: github_document
---


---

```{r, include = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Lists

```{r}
vec_numeric = 5:8
vec_logical = c(TRUE, FALSE, TRUE, TRUE)
```

Lets look at a list

```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000))
)
```

Accessing list items

```{r}
l$vec_numeric
l[[3]]
l[["mat"]]
```


## Loops!

Let's write a `for` loop to take the mean and SD of four samples from a normal distribution

rnorm(n,mean = ?, sd = 1)

```{r}
list_norm = 
  list(
    a = rnorm(20, 5, 4),
    b = rnorm(20, -12, 3),
    c = rnorm(20, 17, .4),
    d = rnorm(20, 100, 1)
  )
```

Here's my function

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Z scores only work for numbers")
  }
  
  if (length(x) < 3) {
    stop("Z scores really only work if you have three or more numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}
```

Let's try to make this work.
- right now I am not saving the results
- do you really want to repeat each input by copying and pasting?
```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
mean_and_sd(list_norm[[4]])
```

Let's a `for` loop instead.

- make it scalable'
-keep track of input and output

1.define your input (in this case "list_norm")
2. output should be of vector type = list and length 4 because 4 samples
3. output is just an empty list
4. i is a placeholder
5. notice that if your vector length (m) exceeds the number of loops in 1:n such that m > n, you will have "null" values in your list 
6. if your n (number of loops) exceeds your input value (length of list_norm) than you will get an error of subscript out of bounds
7.  FYI you can't pipe into a forloop

```{r}
output = vector("list", length = 4)
for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm[[i]])
}
output
```

## can we map??

we can map!! (same output)
- simpler process
- map for this input list and apply this function
- no need to define output list in advance

map(input_name, function )

```{r}
map(list_norm, mean_and_sd)

```

so ... what about other functions?

```{r}
map(list_norm, summary)
```

map variants ...

variants, summary ---> you could easily change your function
will give you a simplified vector of what you were starting out with
 - each time you are getting a dataframe, you could bind rows 
 
 
 you could also define map(list_norm, median) as equal to output to save it FYI 
 
 using dbl and df would help you show #s (changes how they appear) and bind rows respectively
 

```{r}

map(list_norm, median)
map_dbl(list_norm, median)
map_df(list_norm, median)

output = map_df(list_norm, mean_and_sd)

```


## list columns ...
- only issue with dataframes is that you have to use the same # of elements
- your list_norm technically has 4 elements!
- inception time!

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    norm = list_norm
  )
listcol_df[["norm"]]
output = map(listcol_df[["norm"]], mean_and_sd)
```

can we add list columns, and then what
- fyi you could do map_df as well instead of map below
- map across the normal function that I want to map

```{r}
listcol_df %>% 
  mutate(
    m_sd = map(norm, mean_and_sd)
  ) %>% 
  select(-norm)
```

## What about something more realistic...

- when do you actually want to apply the map function in reality?
- when does data with this structure actually come into play? 

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

you could think about converting each weather station id (n = 3) and collapse them so that all the data is specific to each dataframe


let's nest within weather stations...
- R asks you to name it as data
- date:tmin are going to be collapsed in the listcol tibble "data"

```{r}
weather_nest_df = 
  weather_df %>% 
  nest(data = date:tmin)
```


Really is a list column!
- no really go through all

_why not use $ sign?_
- because i don't want to take out my variable from my df
- that's how you make mistakes

_why use [[]]_
So you can troubleshoot -- happens a lot
lol don't use dollar signs though
Most folks who write code using tidyverse tools --> they just don't use $ signs

_look into a whileloop: eh nice to know_

```{r}
weather_nest_df[["data"]]
```

##WHat if you wanted to do an analysis on your dataframe of dataframe? 
i.e. mini regression fitting model of tmax on tmin for an input data frame

- if you give me a df, i can do that 

take out the data column (actually a list col) and the first element
```{r}
weather_nest_df[["data"]][[1]]
lm(tmax ~ tmin, data = weather_nest_df[["data"]][[1]])
lm(tmax ~ tmin, data = weather_nest_df[["data"]][[2]])
lm(tmax ~ tmin, data = weather_nest_df[["data"]][[3]])
```

Let's write a short lil ol function that if you give me a dataframe what regression comes out of that dataframe

...and you can map across this list of dataframes the weather_lm function

- given an input list and a function, 
apply this function to the i to n element of the list
```{r}
weather_lm = function(df) {
  
  lm(tmax ~ tmin, data = df)
  
}
weather_lm(weather_nest_df[["data"]][[1]])

### more scalable
map(weather_nest_df[["data"]], weather_lm)
```

Can i do all this in a tidy way
 - aka not taking it out of the df 
 - want to be able to know how this is linked together not to extract it
 
 1. nested
 2. created a function 
 3. created a listcol
 
 ..This is a lot of work

```{r}
weather_nest_df %>% 
  mutate(
    model = map(data, weather_lm)
  )
```

YUP


##unnesting
get back what you had before ; reverse of nest

```{r}
weather_nest_df %>% 
  unnest(data)
```

## Napoleon!!


Here's my scraping function that works for a single page

```{r}
read_page_reviews = function(url) {
  
  dynamite_html = read_html(url)
  review_titles = 
    dynamite_html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    dynamite_html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  reviews = 
    tibble(
      title = review_titles,
      stars = review_stars,
      text = review_text
    )
  
  reviews
  
}
```

What we did last time:

```{r}
base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_url = str_c(base_url, c(1, 2, 3, 4, 5))
dynamite_reviews = 
  bind_rows(
    read_page_reviews(vec_url[1]),
    read_page_reviews(vec_url[2]),
    read_page_reviews(vec_url[3]),
    read_page_reviews(vec_url[4]),
    read_page_reviews(vec_url[5])
  )


###more tidy and eficient

map(vec_url, read_page_reviews)

####now, to make it more efficient and in a df
###### remember: read_page_reviews = a function you defined and basically generating a dataset --> write a function that takes an input and then maps across a list of inputs and creates an output 
####### notice that for the final product page_url is functionally same as vec_url

napoleon_reviews = 
  tibble(
    page = 1:5, ##this was entered after page_url was tested
    page_url = str_c(base_url, page)
  ) %>% 
  mutate(
    reviews = map(page_url, read_page_reviews)
  )


###OH: when did he nest it? Technically, everything was already unique so no need to nest? You have a column that is all tibbles ---> expand all the inception-dataframes

napoleon_reviews %>% 
  select(-page_url) %>% 
  unnest(reviews)
```

