---
title: "Simulation"
output: github_document
---

```{r, echo = FALSE}
library(tidyverse)

set.seed(1)
```
```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}
```

```{r}
output = vector("list", 100)

for (i in 1:100) {
  output[[i]] = sim_mean_sd(30)
}

sim_results = bind_rows(output)
```

FYI you could have said: .x = sample_size, ~sim_mean_sd(n_obs = .x)

The tilde means that I'm telling you to put it INTO here 


purr package = .x and .y are CUMPOLSORY
you should not have anywhere else called .x or .y

```{r}
sim_results_df = 
  expand_grid(
    sample_size = 30,
    iter = 1:100
  ) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)
```


_What does map allow us to do:_
- take the first element and apply that function and do it all subsequently 

_What does unnest do_
- simple limit theorem - look up 
- to drive all tibbles --> separate 
- what you have is a list column 
( 2 col with x and y respectively)
- by unnest --> you can analyze the dataframe 

_Why use expand grid_
expand_grid:
- I want an input column that is the SAME everywhere
- keeps track of where you are and which variable to use 

_sim_results_df_

- when I gnenerate a 100 datasets, with a true mean of X and a sample mean will vary over time
```{r}
sim_results_df %>% 
  ggplot(aes(x = mu_hat)) + 
  geom_density()
```

_CLT_ 

- Can you model what happens when your sample size gets bigger? - when you map across that sample size column you gor row by row and compute the mean 

```{r}
sim_results_df = 
  expand_grid(
    sample_size = c(30, 60, 120, 240),
    iter = 1:1000
  ) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)
```
_We can now see what is the distribution_

FYI violin plot assumes not a number = x
fct inorder = sample size as it appears in my df
```{r}
sim_results_df %>% 
  mutate(
    sample_size = str_c("N = ", sample_size),
    sample_size = fct_inorder(sample_size)
  ) %>% 
  ggplot(aes(x = sample_size, y = mu_hat)) + 
  geom_violin()
```
```{r}
sim_results_df = 
  expand_grid(
    sample_size = c(30, 60, 120, 240),
    true_sd = c(6, 3),
    iter = 1:1000
  ) %>% 
  mutate(
    estimate_df = 
      map2(.x = sample_size, .y = true_sd, ~sim_mean_sd(n = .x, sigma = .y))
  ) %>% 
  unnest(estimate_df)

```

Above you see that the syntax is 
map2 = function ONLY for two arguments; notice that you have to do it explicitly

_power of simulations is that you can model and test theories etc_ 

```{r}
sim_results_df %>% 
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) %>% 
  ggplot(aes(x = sample_size, y = mu_hat, fill = sample_size)) + 
  geom_violin() + 
  facet_grid(. ~ true_sd)
```
An additional rmd code chunk 
- very specific to a specific code 
- if truly new --> will rerun
- otherwise will save 
- r will not keep track of overwriting existing variables if they are different
{r, cache = TRUE}

