---
title: "iteration"
output: github_document
---


```{r, echo = FALSE}
library(tidyverse)
library(rvest)
```

##Z scores

Let's compute the z - score version of a list of numbers

z score = point estimate - mean of the sample (mu) all over the standard deviation

rnorm is the R function that simulates random variates having a specified normal distribution

```{r}
x_vec = rnorm(25, mean = 7, sd = 4)
  

x_vec - mean(x_vec) / sd(x_vec)
```

*Suppose you want to generate multiple z scores; How to create a function of what I want it to do


* inside of the function it is going to look for x and recognize that there is something to do based on that

* syntax

(name of custom function) = function(ARGUMENTS) {

BODY OF FUNCTION 

}

Here you are using a generic x:

- Instead of putting "z" to have it show, you can have it "return(z)"
- you can save the function itself by labeling it z and that way you can have the return object show as part of your overall function 
```{r}

z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)

  z
}
  

```

you will think it hasnt done anything but now you have created a function called z_scores()

```{r eval = FALSE}

z_scores(x = x_vec)

z_scores(x = 1:10)
z_scores(x = 3)
z_scores(x = "my name is jeff")
```


what if i want to make it fancier

- give me an error if I just have a point estimate (not a sample)
- give me an error if I do not have #s 

```{r}
z_scores = function(x) {
  
  if(!is.numeric(x)) {
    stop("Z scores only work for numbers")
  }
  
  if(length(x) < 3) {
    stop("Z scores really only work if you have more than 3 numbers")
  }
}
```

## Let's have multiple outputs

Let's just get the mean and sd from the vector input

- to make it return both of these objects you have to combine both of these by creating a tibble


```{r}
mean_and_sd = function(x) {
  
  if(!is.numeric(x)) {
    stop("Z scores only work for numbers")
  }
  
  if(length(x) < 3) {
    stop("Z scores really only work if you have more than 3 numbers")
  }
  
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}




```


Now test

```{r}
mean_and_sd(x = x_vec)
mean_and_sd(x = 1:10)
mean_and_sd(x = rbinom(1000, 1, .5))

```

## How to write simulations/ functions that have multiple inputs & outputs

* specifically  writing simulation
* making up data when you have data that is made up
* what if ran this over and over and over --> what is the sample mean and sample sdev

Notice how you can vary the values manually/rerun for the same inputs and each yields diff results because diff sample is pulled 

** important you inserted the mean value and stdard value yourself 

function(ARGUMENTS)

** If I were to rerun below several times, I would get different means and sd as well 
** to make them closer, you would increase the sample size (and to vary could vary e.g. the mean)
** below 3 inputs you care about

```{r}
x_vec = rnorm(n = 2500, mean = 7, sd = 4)

tibble(
  mean = mean(x_vec),
  sd = sd(x_vec)
)
```

Can I do this using a function? DUH.

- below: writing a function that allows you to manipulate any of the inputs e.g. 

function_name = function(ARGUMENTS) {

 CODE TO DO STUFF
}

- BELOW x is a vector being created within the function

-  you are creating default values when your x n_obs is running


also: 



```{r}

sim_mean_sd = function(n_obs, true_mean = 7, true_sd = 4) {

x = rnorm(n_obs, mean = true_mean, sd = true_sd)

tibble(
  mean = mean(x),
  sd = sd(x)
)

}


```
 but does it work?
 
```{r}
sim_mean_sd(n_obs = 25, true_mean = 100, true_sd = 5)
```
 
Do I have to name all the things i have? 

If you do not name, it will assume that you are putting thigns in order i.e sim_mean_sd(25)  assumes n_obs = 25 b/c first argument in your argument

* if you name assumes same order i.e. true mean = 10, n_obs = 25000, sd = 7,

_Same thing_

```{r}
sim_mean_sd(25000, 10, 7)
```

```{r}
sim_mean_sd(true_mean=10, n_obs = 25000, 7)
```


##Fixing bad stuff:


** 1 page of reviews
** Okay, complete, but how would you scale this up to get 10 pages of reviews or 1000?!
** without functions, you would simply change 10x - 1000x from &pageNumber = 1 to n

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=5"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```


## Let's write a function to get reviews

still form function(ARGUMENT) { DO STUFF}

- negate = true (take it away)
- negate it there is a space or ^$

```{r}
read_page_reviews = function(url) {
  
  dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim() %>% 
  str_subset("The media could not be loaded.", negate = TRUE) %>% 
  str_subset("^$", negate = TRUE)

reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text)

reviews 

}
```


## Let's try with a URL 

- now you can vary by a URL link each time and have it read for you

```{r}
 
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=3"

read_page_reviews(url)
```


## What good does this do me?

1. Start with base url that is everything but the page number

_office hours: why do we need to skip a certain page again?_

- for me it doesn't work on pg 4 
- because someone put in an image and the css tag does not work because it is not loadable

```{r}
base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
```

```{r}
vec_url = str_c(base_url, c(1,2,3,4, 5))

dynamite_reviews = 
  bind_rows(
    read_page_reviews(vec_url[1]),
    read_page_reviews(vec_url[2]),
    read_page_reviews(vec_url[3]),
    read_page_reviews(vec_url[4]),
    read_page_reviews(vec_url[5])
  )

```

## Creating a function using LOTR data


- Can you write a function that allows you to vary the range, and movie name

```{r eval = FALSE}
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") %>%
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") %>%
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") %>%
  mutate(movie = "return_king")

lotr_tidy = bind_rows(fellowship_ring, two_towers, return_king) %>%
  janitor::clean_names() %>%
  gather(key = sex, value = words, female:male) %>%
  mutate(race = str_to_lower(race)) %>% 
  select(movie, everything()) 
```


TO 

```{r, eval = FALSE}
lotr_load_and_tidy = function(path, range, movie_name) {
  
  df = readxl::read_excel(path, range = range) %>%
    janitor::clean_names() %>%
    gather(key = sex, value = words, female:male) %>%
    mutate(race = str_to_lower(race),
           movie = movie_name)
  
  df
  
}

lotr_tidy = 
  bind_rows(
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "B3:D6", "fellowship_ring"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "F3:H6", "two_towers"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "J3:L6", "return_king")) %>%
  select(movie, everything()) 
```


## Variable Scoping and names

* above, you were working on functions that were created INSIDE a function

_Does this function exist outside? NO IT STAYS INSIDE THE FUNCTION_

Impact: 
* debugging and writing function quirks
* have you created the rigth thing
* _you may have run it in the environment just to check it and oops you accidentally created a function outside of the function technically because you highlighted it_
* did you make sure you are reusing/recycling the same variable outside of your function 
* _careful becuase you also may have already created a variable outside of your fucntion and are now calling it in the function -- you are not creating the variable but you are telling R to search for that variable in your R studio instance = SCOPING_

_Why is it better to create an input_

_You can return what you want in the tibble, but don't create a new variable_
```{r}
sim_mean_sd = function(n_obs, true_mean = 7, true_sd = 4) {

x_inside__of_function = rnorm(n_obs, true_mean, true_sd)

tibble(
  mean = mean(x),
  sd = sd(x)
)

}
```

